\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
%
%\item Draw the circumcircle of $\triangle ABC$, where 
%
\item Find the value of  the following polynomial at the indicated value of variables 
\begin{align}
p(x) = 5x^2– 3x + 7 \text{  at } x = 1.
\end{align}
\item Verify whether 2 and 0 are zeroes of the polynomial $x^2-2x$.
\item Find $p(0)$, $p(1)$ and $p(2)$ for each of the following polynomials: 
\begin{enumerate}
\item $p(y) = y^2$. 
\item $p(x) = (x – 1) (x + 1)$.
\end{enumerate}
\item Find the roots of the equation  $2x^2– 5x + 3 = 0$ .
\item Find the roots of the quadratic equation $6x^2– x – 2 = 0.$
\item Find the roots of the quadratic equation $3x^2 -2 \sqrt{6}x+ 2 = 0$.
%\item Verify whether the following are zeroes of the polynomial, indicated against them. (i) p(x) = 3x + 1, x =
%\begin{enumerate}
%
%\item $ p(x) = x^2-1, x = 1, -1$
%\item $ p(x) = 5x -\pi, x = \frac{4}{5}$
%\item $ p(x) = \brak{x+1} \brak{x-2}, x = -1,2$
%\item $ p(x) = x^2, x = 0$.
%\item $ p(x) = 3x^2-1, x = -\frac{1}{\sqrt{3}}, \frac{2}{\sqrt{3}}$.
%
\item Factorise $6x^2+ 17x + 5$.
\item Factorise $y^2 – 5y + 6$.
\item Find the zeroes of the quadratic polynomial $x^2+7x+10$ and verify the relationship between the zeroes and the coefficients.
\item Find the zeroes of the polynomial $x^2-3$ and verify the relationship between the zeroes and the coefficients.
\item Find a quadratic polynomial, the sum and product of whose zeroes are – 3 and 2, respectively.
%
\item Find the roots of the equation $5x^2  – 6x – 2 = 0 $.
\item Find the roots of $4x^2 + 3x + 5 = 0 $.
\item Find the roots of the following quadratic equations, if they exist.
\begin{enumerate}
\item 	$3x^2-5x+2 = 0$
\item 	$x^2+4x+5 = 0$
\item 	$2x^2-2\sqrt{2}x+1 = 0$
\end{enumerate}
%
\item Find the discriminant of the quadratic equation $2x^2-4x+3 = 0$
hence find the nature of its roots.
\item Find the discriminant of the quadratic equation $3x^2-2x+\frac{1}{3} = 0$
hence find the nature of its roots.
\item Solve $x^2+ 2 = 0 $.
\item Solve $x^2+ x+1 = 0 $.
\item Solve $\sqrt{5}x^2+ x+\sqrt{5} = 0 $.
%
\item Find the coordinates of the focus, axis, the equation of the directrix and latus rectum of the parabola $y^2 = 8x$.
%
\item Find the equation of the parabola with focus \myvec{2\\0} and directrix $\myvec{1 & 0}\vec{x} = -2$.\item Find the equation of the parabola with vertex at \myvec{0\\ 0} and focus at \myvec{0\\ 2}.
\item Find the equation of the parabola which is symmetric about the y-axis, and passes through the point \myvec{2\\–3}.
\item Find the coordinates of the foci, the vertices, the length of major axis, the minor axis, the eccentricity and the latus rectum of the ellipse 
%
\begin{align}
\vec{x}^T\myvec{\frac{1}{25} & 0 \\ 0 & \frac{1}{9}}\vec{x} = 1
\end{align}
%
\item Find the coordinates of the foci, the vertices, the lengths of major and minor axes and the eccentricity of the ellipse 
%
\begin{align}
\vec{x}^T\myvec{9 & 0 \\ 0 & 4}\vec{x} = 36
\end{align}
%
\item Find the equation of the ellipse whose vertices are $\myvec{\pm 13\\ 0}$ and foci are $\myvec{\pm 5\\ 0}$.
%
\item Find the equation of the ellipse, whose length of the major axis is 20 and foci are $\myvec{0\\ \pm 5}$
%
\item Find the equation of the ellipse, with major axis along the x-axis and passing through the points \myvec{4\\ 3} and \myvec{– 1\\4}.
%
\item Find the coordinates of the foci and the vertices, the eccentricity,the length of the latus rectum of the hyperbolas
\begin{enumerate}
\item 
$
\vec{x}^T\myvec{\frac{1}{9} & 0 \\ 0 & -\frac{1}{16}}\vec{x} = 1
$
\item 
$
\vec{x}^T\myvec{1 & 0 \\ 0 & -16}\vec{x} = 16
$
\end{enumerate}
\item Find the equation of the hyperbola with  vertices $\myvec{0 \\ \pm \frac{\sqrt{11}}{2}}$, foci $\myvec{ 0\\ \pm 3}$
\item Find the equation of the hyperbola with   foci $\myvec{ 0\\ \pm 12}$ and length of latus rectum 36.
%
\item Find the equation of all lines having slope 2 and being tangent to the curve
\begin{align}
y + \frac{2}{x-3} = 0
\end{align}
%
\item Find the point at which the tangent to the curve $y = \sqrt{4x-3}-1$ has its 
slope $\frac{2}{3}$.
%
\item Find the roots of the following equations:
\begin{enumerate}
\item  $x + \frac{1}{x} = 3, x \ne =0 $
\item  $ \frac{1}{x} + \frac{1}{x-2}=3, x\ne =0, 2 $
\end{enumerate}
%
\item Find points on the curve 
$
\vec{x}^T\myvec{\frac{1}{4} & 0 \\ 0 & \frac{1}{25}}\vec{x} = 1
$
at which the tangents are 
\begin{enumerate}
\item parallel to x-axis
\item parallel to y-axis
\end{enumerate}
 \item Find the equation of the normal to the curve $x^2= 4y$
which passes through the point \myvec{1\\ 2}.
%
\item Find the area enclosed by the ellipse
$
\vec{x}^T\myvec{\frac{1}{a^2} & 0 \\ 0 & \frac{1}{b^2}}\vec{x} = 1
$
%
\item Find the area of the region bounded by the curve $y = x^2$
and the line $y = 4$.
%
\item Find the area bounded by the ellipse
$
\vec{x}^T\myvec{\frac{1}{a^2} & 0 \\ 0 & \frac{1}{b^2}}\vec{x} = 1
$
and $x = ae$, where, $b^2 = a^2 (1 – e^2 )$ and $e < 1$.
%
\item Prove that the curves $y^2 = 4x$ and $x^2 = 4y$ divide the area of the square bounded by $x = 0, x = 4, y =4$ and $y = 0$ into three equal parts.
%
\item Find the area of the region
\begin{align}
\cbrak{\brak{x,y} = 0\le y\le x^2+1, 0\le y \le x+1, 0 \le x \le 2}
\end{align}
\item Find the interals in which the function 
\begin{align}
f(x)  = x^2-4x+6
\end{align}
%
is 
\begin{enumerate}
\item increasing
\item decreasing.
\end{enumerate}
%
\item Find the shortest distance of the point $\myvec{0\\c}$ from the parabola $y = x^2$, where $\frac{1}{2} \le c \le 5$.
%
\item An apache helicopter of enemy is flying along the curve given by $y = x^2+7$.  A soldier, placed at \myvec{3\\7}, wants to shoot down the helicopter when it is nearest to him.  Find  the nearest distance.
%
\item Examine whether the function $f$ given by $f(x) = x^2$ is continuous at $x = 0$.
%
\item Discuss the continuity of the function $f$ defined by 
%
\begin{align}
f(x)  = 
\begin{cases}
x & x \ge 0
\\
x^2 & x < 0
\end{cases}
\end{align}
%
\item Verify Rolle's theorem for the function $y = x^2+2, a = -2$ and $b = 2$.
\item Verify Mean Value Theorem for the function $f(x) = x^2$ in the interval $\sbrak{2,-4}$.
%\end{align}
\item Find the derivative of $f(x) = x^2$.
\item Find the derivative of $ x^2 - 2$ at $x = 10$.
\item Find the derivative of $ \brak{x-1} \brak{x-2}$.
%
%
\item Find 
\begin{align}
\int_{0}^{2} \brak{x^2+1}\,dx
\end{align}
%
as a limit of a sum.
\item Evaluate the following integral:
%
\begin{align}
\int_{2}^{3}x^2 \,dx
\end{align}
%
\item Form the differntial equation representing the family of ellipses having foci on x-axis and cenre at the origin.
%
\item Form the differntial equation representing the family of parabolas having vertex at origin and axis along positive direction of x-axis.
\item Form a differntial equation representing the following family of curves
%
\begin{align}
y^2 = a\brak{b^2-x^2}
\end{align}
%
\end{enumerate}
