\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
%
\item For the AP :
$\frac{3}{2},\frac{1}{2},-\frac{1}{2},-\frac{3}{2},.....$ write the first term a and the common difference d.
\item Which of the following list of numbers form an AP? If they form an AP,
write the next two terms :
\begin{enumerate}
\item 4,10,16,22,...
\item 1,-1,-3,-5,...
\item -2,2,-2,2,-2,...
\item 1,1,1,2,2,2,3,3,3,...
\end{enumerate}
\item Find the 10th term of the AP : 2, 7, 12, . . .
\item Which term of the AP : 21, 18, 15, . . . is – 81? Also, is any term 0? Give reason for your answer.
\item Determine the AP whose 3rd term is 5 and the 7th term is 9.
\item Check whether 301 is a term of the list of numbers 5, 11, 17, 23, . . .
\item How many two-digit numbers are divisible by 3?
\item Find the 11th term from the last term (towards the first term) of the
AP : 10, 7, 4, . . ., – 62.
\item A sum of \rupee 1000 is invested at 8$\%$ simple interest per year. Calculate the interest at the end of each year. Do these interests form an AP? If so, find the interest at the end of 30 years making use of this fact.
\item In a flower bed, there are 23 rose plants in the first row, 21 in the
second, 19 in the third, and so on. There are 5 rose plants in the last row. How many rows are there in the flower bed?
\item Find the sum of the first 22 terms of the AP : 8, 3, –2, . . .
\item If the sum of the first 14 terms of an AP is 1050 and its first term is 10, find the 20th term.
\item How many terms of the AP : 24, 21, 18, . . . must be taken so that their
sum is 78?
\item Find the sum of :\\
(i) the first 1000 positive integers\\
(ii) the first n positive integers.\\
\item Find the sum of first 24 terms of the list of numbers whose $n^{th}$ term is given by $a_n = 3 + 2n$
\item A manufacturer of TV sets produced 600 sets in the third year and 700
sets in the seventh year. Assuming that the production increases uniformly by a fixed number every year, find :\\
(i) the production in the 1st year\\
(ii) the production in the 10th year\\
(iii) the total production in first 7 years.
\end{enumerate}
%\end{document}
    
