\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Write the first three terms in each of the following sequences defined by the following:
(i) $a n = 2n + 5,$\\
(ii) $a_n = \frac{n-3}{4}$
\item What is the $20^{th}$ term of the sequence defined by
$a_n = (n - 1) (2 - n) (3 + n)?$
\item Let the sequence $a_n$ be defined as follows: \\$a_1 = 1, \\a_n = a_{n - 1} + 2 for n \geq 2.$\\ Find first five terms and write corresponding series.
\item In an A.P. if $m^{th}$ term is n and the $n^{th}$ term is m, where $m \neq n$, find the $p^{th}$
term.
\item If the sum of n terms of an A.P. is\\ nP + $\frac{1}{2}n(n-1)Q,$ where P and Q are constants, find the common differences.
\item The sum of n terms of two arithmetic progressions are in the ratio (3n + 8) : (7n + 15). Find the ratio of their $12^{th}$ terms.
\item The income of a person is Rs. 3,00,000, in the first year and he receives an increase of Rs.10,000 to his income per year for the next 19 years. Find the total amount, he received in 20 years.
\item Insert 6 numbers between 3 and 24 such that the resulting sequence is an A.P.
\item Find the 10 and n terms of the G.P. 5, 25,125,... .
\item Which term of the G.P., 2,8,32, ... up to n terms is 131072?
\item In a G.P., the $3^{rd}$ term is 24 and the $6^{th}$ term is 192.Find the $10^{th}$ term.
\item Find the sum of first n terms and the sum of first 5 terms of the geometric series $1+\frac{2}{3}+\frac{4}{9}+......$
\item How many terms of the G.P.$3, \frac{3}{2}, \frac{3}{4},.....$ are needed to give the sum 
$\frac{3069}{512} ?$
\item The sum of first three terms of a G.P. is $\frac{13}{12}$ and their product is -1. Find the common ratio and the terms.
\item Find the sum of the sequence 7, 77, 777, 7777, ... to n terms.
\item A person has 2 parents, 4 grandparents, 8 great grandparents, and so on. Find the number of his ancestors during the ten generations preceding his own.
\item Insert three numbers between 1 and 256 so that the resulting sequence is a G.P.
\item If A.M. and G.M. of two positive numbers a and b are 10 and 8, respectively, find the numbers.
\item Find the sum to n terms of the series: 5 + 11 + 19 + 29 + 41...
\item Find the sum to n terms of the series whose $n^{th}$ term is n(n+3).
\item If $p^{th}, q^{th}, r^{th}$ and $s^{th}$ terms of an A.P. are in G.P, then show that (p - q), (q - r), (r - s) are also in G.P.
\item If a, b, c are in G.P. and $a^\frac{1}{x} = b^\frac{1}{y} = c^\frac{1}{z},$ prove that x, y, z are in A.P.
\item If a, b, c, d and p are different real numbers such that $(a^2 + b^2 + c^2 ) p^2 - 2(ab + bc + cd) p + (b^2 + c^2 + d^2 ) \leq 0,$ then show that a, b, c and d are in G.P.
\item If p, q, r are in G.P. and the equations, $px^2 + 2qx + r = 0$ and $dx^2 + 2ex + f = 0$ have a common root, then show that $\frac{d}{p}, \frac{e}{q}, \frac{f}{r}$ are in A.P.
\end{enumerate}
%\end{document}
    
