\item A survey was conducted by a group of students as a part of their environment awareness
programme, in which they collected the following data in Table \ref{table:2.2.1}
regarding the number of plants in
20 houses in a locality. Find the mean number of plants per house.
\begin{table}[!ht]
\centering
\resizebox{\columnwidth}{!}{%
%{\small
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
Number of plants &0-2&2-4&4-6&6-8&8-10&10-12&12-14\\
\hline
Number of houses&1&2&1&5&6&2&3\\
\hline
\end{tabular}
%}
}
\caption{}
\label{table:2.2.1}
\end{table}
\\
\solution
%\input{./solutions/1-10/chapters/statics/problem1/solution.tex}
\item Consider the following distribution of daily wages of 50 workers of a factory.
%\begin{tabular}{|c|c|c|c|c|c|}
%\hline
%Daily wages (in rupees) &500-520&520-540&540-560&560-580&580-600\\
%\hline
%Number of workers&12&14&8&6&10&\\
%\hline
%\end{tabular}\\
Find the mean daily wages of the workers of the factory by using an appropriate method.
\item The following distribution shows the daily pocket allowance of children of a locality.
The mean pocket allowance is Rs 18. Find the missing frequency f.
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
Daily pocket allowance(in rupees) &11-13&13-15&15-17&17-19&19-21&21-23&23-25\\
\hline
Number of children&7&6&9&13&f&5&4\\
\hline
\end{tabular}\\
\item Thirty women were examined in a hospital by a doctor and the number of heartbeats per
minute were recorded and summarised as follows. Find the mean heartbeats per minute
for these women, choosing a suitable method.
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
Number of heartbeats for minute &65-68&68-71&71-74&74-77&77-80&80-83&83-86\\
\hline
Number of women&2&4&3&8&7&4&2\\
\hline
\end{tabular}\\
\item In a retail market, fruit vendors were selling mangoes kept in packing boxes. These
boxes contained varying number of mangoes. The following was the distribution of
mangoes according to the number of boxes.
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Number of mangoes&50-52&53-55&56-58&59-61&62-64\\
\hline
Number of boxes&15&110&135&115&25\\
\hline
\end{tabular}\\
\par Find the mean number of mangoes kept in a packing box. Which method of finding
the mean did you choose?
\item The table below shows the daily expenditure on food of 25 households in a locality.
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Daily expenditure(in rupees)&100-150&150-200&200-250&250-300&300-350 \\
\hline
Number of households&4&5&12&2&2\\
\hline
\end{tabular}\\
\par Find the mean daily expenditure on food by a suitable method.
\item To find out the concentration of $so_2$ in the air (in parts per million, i.e., ppm), the data was collected for 30 localities in a certain city and is presented below:
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Concentration of $SO_2$ (in ppm)&0.00-0.04&0.04-0.08&0.08-0.12&0.12-0.16&0.16-0.20& 
0.20-0.24 \\
\hline
Frequency&4&9&9&2&4&2\\
\hline
\end{tabular}\\
\par Find the mean concentration of $SO_2$ in the air.
\item A class teacher has the following absentee record of 40 students of a class for the whole
term. Find the mean number of days a student was absent.
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
Number of days&0-6&6-10&10-14&14-20&20-28&28-38&38-40 \\
\hline
Number of students&11&10&7&4&4&3&1\\
\hline
\end{tabular}\\
\item The following table gives the literacy rate (in percentage) of 35 cities. Find the mean
literacy rate.
%\begin{tabular}{|c|c|c|c|c|}
%\hline
%literacy(in percentage)&45-55&55-65&65-75&75-85&85-95\\
%\hline
%Number of cities&3&10&11&8&3\\
%\hline
%\end{tabular}\\\\
{\Large \textbf{EXERCISE 14.2}}\\
\item The following table shows the ages of the patients admitted in a hospital during a year:
%\begin{tabular}{|c|c|c|c|c|}
%\hline
%Age (in years) &5-15&15-25&25-35&35-45&45-55&55-65\\
%\hline
%Number of patients&6&11&21&23&145\\
%\hline
%\end{tabular}\\
Find the mode and the mean of the data given above. Compare and interpret the two
measures of central tendency.
\item The following data gives the information on the observed lifetimes (in hours) of 225
electrical components :
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
Lifetimes (in hours)&0-20&20-40&40-60&60-80&80-&100&100-120\\
\hline
Frequency&10&35&52&61&38&29\\
\hline
\end{tabular}\\
Determine the modal lifetimes of the components.
\item The following data gives the distribution of total monthly household expenditure of 200
families of a village. Find the modal monthly expenditure of the families. Also, find the
mean monthly expenditure :
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Expenditure (in rupees)&1000-1500&1500-2000&2000-2500&2500-3000&3000-3500&3500-4000&4000-4500& 4500-5000\\
\hline
Number of families&24&40&33&28&30&22&16&7\\
\hline
\end{tabular}\\
\item The following distribution gives the state-wise teacher-student ratio in higher
secondary schools of India. Find the mode and mean of this data. Interpret the two
measures.
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Number of students per teacher&15-20&20-25&25-30&30-35&35-40&40-45&45-50&50-55\\
\hline
Number of states / U.T.&3&8&9&10&3&0&0&2\\
\hline
\end{tabular}\\
\item The given distribution shows the number of runs scored by some top batsmen of the
world in one-day international cricket matches.
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Runs scored&3000-4000&4000-5000&5000-6000&6000-7000&7000-8000&8000-9000&9000-10000&10000- 11000\\
\hline
Number of batsmen&4&18&9&7&6&3&1&1\\
\hline
\end{tabular}\\
Find the mode of the data.
\item A student noted the number of cars passing through a spot on a road for 100
periods each of 3 minutes and summarised it in the table given below. Find the mode
of the data :
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Number of cars&0-10&10-20&20-30&30-40&40-50&50-60&60-70&70-80\\
\hline
Frequency&7&14&13&12&20&11&15&8\\
\hline
\end{tabular}\\\\
{\Large \textbf{EXERCISE 14.3}}
\item The following frequency distribution gives the monthly consumption of electricity of
68 consumers of a locality. Find the median, mean and mode of the data and compare
them.
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Monthly consumption (in units)&65-85&85-105&105-125&125-145&145-165&165-185&185-205\\
\hline
Number of consumers&4&5&13&20&14&8&4\\
\hline
\end{tabular}\\
\item If the median of the distribution given below is 28.5, find the values of x and y.
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Class interval&0-10&10-20&20-30&30-40&40-50&50-60& Total\\
\hline
Frequency&5&x&20&15&y&5&60\\
\hline
\end{tabular}\\
\item A life insurance agent found the following data for distribution of ages of 100 policy
holders. Calculate the median age, if policies are given only to persons having age 18
years on wards but less than 60 year.
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
Age (in years)&Below 20&Below 25&Below 30&Below 35 Below 40& Below 45& Below 50& Below 55& Below 60\\
\hline
Number of policy holders&2&6&24&45&78&89&92&98&100\\
\hline
\end{tabular}\\
\item The lengths of 40 leaves of a plant are measured correct to the nearest millimetre, and
the data obtained is represented in the following table :
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
Length (in mm)&118-126&127-135&136-144&145-153&154-162&163-171&172-180\\
\hline
Number of leaves&2&6&24&45&78&89&92&98&100\\
\hline
\end{tabular}\\
Find the median length of the leaves.
(Hint : The data needs to be converted to continuous classes for finding the median,
since the formula assumes continuous classes. The classes then change to
117.5 - 126.5, 126.5 - 135.5, . . ., 171.5 - 180.5.)
%\item 
%The following table gives the distribution of the life time of 400 neon lamps :
%\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
%\hline
%Life time (in hours)&1500-2000&2000-2500&2500-3000&3000-3500&3500-4000&4000-4500&4500-5000\\
%\hline
%Number of lamps&14&56&60&86&74&62&48\\
%\hline
%\end{tabular}\\
%Find the median life time of a lamp.
%\input{./solutions/40-50/statistics/chapters/Q41/problem.tex}
%\solution
%\input{./solutions/40-50/statistics/chapters/Q41/solution.tex}
%\item 
%\input{./solutions/40-50/statistics/chapters/Q42/problem.tex}
%\solution
%\input{./solutions/40-50/statistics/chapters/Q42/solution.tex}

%100 surnames were randomly picked up from a local telephone directory and the
%frequency distribution of the number of letters in the English alphabets in the surnames
%was obtained as follows:
%\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
%\hline
%Number of letters&1-4&4-7&7-10&10-13&13-16&16-19\\
%\hline
%Number of surnames&6&30&40&16&4&4\\
%\hline
%\end{tabular}\\
%Determine the median number of letters in the surnames. Find the mean number of
%letters in the surnames? Also, find the modal size of the surnames.
%\item 
%\input{./solutions/40-50/statistics/chapters/Q43/problem.tex}
%\solution
%\input{./solutions/40-50/statistics/chapters/Q43/solution.tex}
\item The distribution below in Table \ref{table:statexq22} gives the weights of 30 students of a class. Find the median
weight of the students.
\begin{table}[ht]
	\begin{center}
    	\input{./solutions/20-30/tables/statistics/exercises/stat_ex_q22_que.tex}
	\caption{Frequency distribution of the weights of students}
	\label{table:statexq22}
	\end{center}
	\end{table}
\solution
\input{./solutions/20-30/chapters/statistics/exercises/docq22.tex}
%\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
%\hline
%Weight (in kg)&40-45&45-50&50-55&55-60&60-65&65-70&70-75\\
%\hline
%Number of students&2&38&6&6&3&2\\
%\hline
%\end{tabular}\\\\
%{\Large \textbf{EXERCISE 14.4}}
\item The following distribution in Table \ref{table:stat_ex_q23_quetable2} gives the daily income of 50 workers of a factory.
Convert the distribution above to a less than type cumulative frequency distribution,
and draw its ogive.
	\begin{table}[ht]
\centering
    	\input{./solutions/20-30/tables/statistics/exercises/stat_ex_q23_que.tex}
	\caption{Wages obtained by workers}
	\label{table:stat_ex_q23_quetable2}
	\end{table}
\\
\solution
\input{./solutions/20-30/chapters/statistics/exercises/docq23.tex}
%\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
%\hline
%Daily income (in rupees)&100-120&120-140&140-160&160-180&180-200\\
%\hline
%Number of workers&12&14&8&6&10\\
%\hline
%\end{tabular}\\
%\item 
%\input{./solutions/40-50/statistics/chapters/Q44/problem.tex}
%\solution
%\input{./solutions/40-50/statistics/chapters/Q44/solution.tex}
\item During the medical check-up of 35 students of a class, their weights were recorded as in Table
	\ref{table:stat_ex_q24_quetable9}. Draw a less than type ogive for the given data. Hence obtain the median weight from
the graph and verify the result by using the formula.
	\begin{table}[ht!]
\centering
    	\input{./solutions/20-30/tables/statistics/exercises/stat_ex_q24_que.tex}
	\caption{Frequency distribution of the weights of students}
	\label{table:stat_ex_q24_quetable9}
	\end{table}
\\
\solution
\input{./solutions/20-30/chapters/statistics/exercises/docq24.tex}

%follows:
%\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
%\hline
%Weight (in kg)&Less than 38&Less than 40&Less than 42&Less than 44&Less than 46&Less than 48& Less than 50&Less than 52\\
%\hline
%Number of students&0&3&5&9&14&28&32&35\\
%\hline
%\end{tabular}\\
%\item 
%\input{./solutions/40-50/statistics/chapters/Q45/problem.tex}
%\solution
%\input{./solutions/40-50/statistics/chapters/Q45/solution.tex}
\item The following table gives production yield per hectare of wheat of 100 farms of a village.
Change the distribution to more than type distribution and draw its ogive.
	\begin{table}[ht]
	\begin{center}
    	\input{./solutions/20-30/tables/statistics/exercises/stat_ex_q25_que.tex}
	\caption{production yield per hectare of wheat of 100 farms}
	\label{table:stat_ex_q25_table4}
	\end{center}
	\end{table}
%\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
%\hline
%Production yield(in kg/ha)&50-55&55-60&60-65&65-70&70-75&75-80
%\\
%\hline
%Number of farms&2&8&12&24&38&16\\
%\hline
%\end{tabular}\\
%%        
\\
\solution
\input{./solutions/20-30/chapters/statistics/exercises/docq25.tex}
