% \renewcommand{\theequation}{\theenumi}
% \begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
% \numberwithin{equation}{enumi}

\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}


\item How many times must a man toss a fair coin so that the probability of having at least one head is more than 90$\%$?\\
\item An experiment succeeds twice as often as it fails. Find the probability that in the next six trials, there will be at least 4 successes.\\
\solution
\input{solutions/3/3.2.tex}

\item Suppose X has a binomial distribution . Show that X = 3 is the most likely outcome.\\
\solution
\input{solutions/3/3.3.tex}
(Hint : P(X = 3) is the maximum among all P($x_i$), $x_i$= 0,1,2,3,4,5,6)\\
\item The probability that a bulb produced by a factory will fuse after 150 days of use
is 0.05. Find the probability that out of 5 such bulbs\\
(i) none\\
(ii) not more than one\\
(iii) more than one\\
(iv) at least one\\
will fuse after 150 days of use.\\
\solution
\input{solutions/3/3.4.tex}

\item Find the mean number of heads in three tosses of a fair coin.\\
\solution
\input{solutions/3/3.5.tex}

\item Find the probability distribution of\\
(i) number of heads in two tosses of a coin.\\
(ii) number of tails in the simultaneous tosses of three coins.\\
(iii) number of heads in four tosses of a coin.\\
\solution
\input{solutions/3/3.6.tex}

\item Let X represent the difference between the number of heads and the number of tails obtained when a coin is tossed 6 times. What are possible values of X?\\
\item Six balls are drawn successively from an urn containing 7 red and 9 black balls. Tell whether or not the trials of drawing balls are Bernoulli trials when after each draw the ball drawn is\\
(i) replaced \\
(ii) not replaced in the urn.\\
\solution
\input{solutions/3/3.8.tex}

\item If a fair coin is tossed 10 times, find the probability of
\begin{enumerate}
\item  exactly six heads
\item  at least six heads
\item  at most six  heads
\end{enumerate}
\solution
\input{./solutions/20-10/prob/chapters/exam41/solution.tex}

\item Ten eggs are drawn successively with replacement from a lot containing 10$\%$ defective eggs. Find the probability that there is at least one defective egg.\\
\solution
\input{./solutions/20-10/prob/chapters/exam42/solution.tex}

\item Find the mean of the Binomial distribution B(4,$\frac{1}{3}$).
\\
\solution
\input{./solutions/20-10/prob/chapters/exam44/solution.tex}

\item The probability of a shooter hitting a target is $\frac{3}{4}$. How many minimum
number of times must he/she fire so that the probability of hitting the target at least
once is more than 0.99?
\\
\solution
\input{./solutions/20-10/prob/chapters/exam45/solution.tex}

\item Three coins are tossed simultaneously. Consider the event E "three heads or three tails", F "at least two heads" and G "at most two heads". Of the pairs (E,F), (E,G) and (F,G), which are independent? which are dependent?\\
\solution
\input{./solutions/20-30/chapters/prob/examples/docq22.tex}
\item A die is tossed thrice. Find the probability of getting an odd number at least once.\\
\\
\solution
\input{./solutions/40-50/probability/chapters/Q40/solution.tex}
\item A game consists of tossing a one rupee coin 3 times and noting its outcome each time. Hanif wins if all the tosses give the same result i.e., three heads or three tails, and loses otherwise. Calculate the probability that Hanif will lose the game.
\\
\solution
\input{./solutions/10-1/prob/exer4/solution.tex}
\item A die is thrown twice. What is the probability that\\
\begin{enumerate}[label=(\roman*)]
\item  5 will not come up either time? \\
\item  5 will come up at least once?\\
\end{enumerate}
Hint : Throwing a die twice and throwing two dice simultaneously are treated as the
same experiment
\\
\solution
\input{./solutions/10-1/prob/exer5/solution.tex}
\item A die is thrown again and again until three sixes are obtained. Find the probability of obtaining the third six in the sixth throw of the die.\\
\solution
\input{solutions/3/3.17.tex}
%
\item Find the probability of throwing at most 2 sixes in 6 throws of a single die.\\
\solution
\input{solutions/3/3.18.tex}
%
\item In a box containing 100 bulbs, 10 are defective. The probability that out of a
sample of 5 bulbs, none is defective is
\begin{enumerate}
\item $10^{-1}$
\item $\brak{\frac{1}{2}}^5$
\item $\brak{\frac{9}{10}}^5$
\item $\frac{9}{10}$
\end{enumerate}
%
\solution
\input{solutions/3/3.19.tex}
\item In a hurdle race, a player has to cross 10 hurdles. The probability that he will
clear each hurdle is $\frac{5}{6}$. What is the probability that he will knock down fewer than 2 hurdles?\\
\solution 
\input{prob/solutions/1/3/solution.tex}
\item Suppose that 90$\%$ of people are right-handed. What is the probability that
at most 6 of a random sample of 10 people are right-handed?\\
\solution
\input{solutions/1/1.4.tex}
\item The probability that a student is not a swimmer is $\frac{1}{5}$. Then the probability that out of five students, four are swimmers is\\
\begin{enumerate}
\item $\comb{5}{4}\brak{\frac{4}{5}}^4 \frac{1}{5}$
\item $\brak{\frac{4}{5}}^4 \frac{1}{5}$
\item $\comb{5}{1}\brak{\frac{4}{5}}^4 \frac{1}{5}$
\item None of these
\end{enumerate}
\solution
\input{solutions/1/1.5.tex}
%
\item A die is thrown 6 times. If ‘getting an odd number’ is a success, what is the probability of\\
(i) 5 successes?\\
(ii) at least 5 successes?\\
(iii) at most 5 successes?\\
%
\solution
\input{solutions/3/3.22.tex}
\item A bag consists of 10 balls each marked with one of the digits 0 to 9. If four balls are drawn successively with replacement from the bag, what is the probability that none is marked with the digit 0?\\
\solution
\input{solutions/4/4.7.tex}
%
\item An urn contains 25 balls of which 10 balls bear a mark 'X' and the remaining 15 bear a mark 'Y'. A ball is drawn at random from the urn, its mark is noted down and it is replaced. If 6 balls are drawn in this way, find the probability that\\
(i) all will bear 'X' mark.\\
(ii) not more than 2 will bear 'Y' mark.\\
(iii) at least one ball will bear 'Y' mark.\\
(iv) the number of balls with 'X' mark and 'Y' mark will be equal.\\
\solution
\input{solutions/5/5.7.tex}

\item It is known that 10$\%$ of certain articles manufactured are defective. What is the probability that in a random sample of 12 such articles, 9 are defective?\\
\solution $X = B \brak{n,p}$ with $n=12$ and $p=\frac{1}{10}$.  Hence, the desired probability is
%
\begin{align}
  \implies\Pr\brak{X=9} &={12 \choose 9}\times\brak{\frac{1}{10}}^9\times\brak{\frac{9}{10}}^{3} \\  &=\frac{16038}{10^{11}}
\end{align}
\item On a multiple choice examination with three possible answers for each of the five questions, what is the probability that a candidate would get four or more correct answers just by guessing ?
\\
\solution
\input{solutions/5/5.8.tex}

\item Five cards are drawn successively with replacement from a well shuffled deck of 52 cards. What is the probability that\\
(i) all the five cards are spades?\\
(ii) only 3 cards are spades?\\
(iii) none is a spade?\\
\solution 
\input{solutions/5/5.8-1.tex}

\item Two dice are thrown simultaneously. If X denotes the number of sixes, find the
expectation of X.\\
\solution
\input{solutions/4/4.11.tex}
\\
\item Find the variance of the number obtained on a throw of an unbiased die.\\
\input{solutions/5/5.30.tex}
\item A bag contains 2 white and 1 red balls. One ball is drawn at random and then put back in the box after noting its colour. The process is repeated again. If X denotes the number of red balls recorded in the two draws, describe X.\\
\input{solutions/5/5.25.tex}
\item Find the probability of throwing at most 2 sixes in 6 throws of a single die.\\
\solution
\input{solutions/4/4.6.tex}
\end{enumerate}


