\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}


\item Bag I contains 3 red and 4 black balls and Bag II contains 4 red and 5 black balls. One ball is transferred from Bag I to Bag II and then a ball is drawn from Bag II. The ball so drawn is found to be red in colour. Find the probability that the transferred ball is black.\\
\item Suppose we have four boxes A,B,C and D containing coloured marbles as given below:\\
\\$\begin{tabular}{||c c c c||} 
 \hline
 Box & Red & White & Black \\
 \hline
 A & 1 & 6 & 3 \\
 \hline
 B & 6 & 2 & 2 \\
 \hline
 C & 8 & 1 & 1 \\
 \hline
 D & 0 & 6 & 4 \\
 \hline
\end{tabular}$\\
\\One of the boxes has been selected at random and a single marble is drawn from
it. If the marble is red, what is the probability that it was drawn from box A?, box B?,
box C?\\
\solution 
\input{solutions/2/2.2.tex}

\item Assume that the chances of a patient having a heart attack is 40$\%$. It is also
assumed that a meditation and yoga course reduce the risk of heart attack by 30$\%$ and prescription of certain drug reduces its chances by 25$\%$. At a time a patient can choose any one of the two options with equal probabilities. It is given that after going through one of the two options the patient selected at random suffers a heart attack. Find the probability that the patient followed a course of meditation and yoga?\\
\solution
\input{solutions/2/2.3.tex}
\item Suppose that 5$\%$ of men and 0.25$\%$ of women have grey hair. A grey haired person is selected at random. What is the probability of this person being male? Assume that there are equal number of males and females.\\
\solution
\input{solutions/2/2.4.tex}
%\input{solutions/cs21resch01001/2.4.tex}

\item A couple has two children,\\
(i) Find the probability that both children are males, if it is known that at least one of the children is male.\\
(ii) Find the probability that both children are females, if it is known that the elder child is a female.\\
\item A manufacturer has three machine operators A, B and C. The first operator A
produces 1$\%$ defective items, where as the other two operators B and C produce 5$\%$ and 7$\%$ defective items respectively. A is on the job for 50$\%$ of the time, B is on the job for 30$\%$ of the time and C is on the job for 20$\%$ of the time. A defective item is produced, what is the probability that it was produced by A?\\
\solution
\input{solutions/2/2.6.tex}

\item A factory has two machines A and B. Past record shows that machine A produced 60$\%$ of the items of output and machine B produced 40$\%$ of the items. Further, 2$\%$ of the items produced by machine A and 1$\%$ produced by machine B were defective. All the items are put into one stockpile and then one item is chosen at random from this and is found to be defective. What is the probability that it was produced by machine B?\\
%
\solution
\input{solutions/2/2.7.tex}
\item Two groups are competing for the position on the Board of directors of a corporation. The probabilities that the first and the second groups will win are 0.6 and 0.4 respectively. Further, if the first group wins, the probability of introducing a new product is 0.7 and the corresponding probability is 0.3 if the second group wins. Find the probability that the new product introduced was by the second group.\\
\item A laboratory blood test is 99$\%$ effective in detecting a certain disease when it is in fact, present. However, the test also yields a false positive result for 0.5$\%$ of the healthy person tested (i.e. if a healthy person is tested, then, with probability 0.005, the test will imply he has the disease). If 0.1 percent of the population actually has the disease, what is the probability that a person has the disease given that his test result is positive?\\
\item A family has two children. What is the probability that both the children are boys given that at least one of them is a boy?\\
%
\solution
\input{solutions/2/2.10.tex}
\item Ten cards numbered 1 to 10 are placed in a box, mixed up thoroughly and then one card is drawn randomly. If it is known that the number on the drawn card is more than 3, what is the probability that it is an even number?\\
\solution
\input{solutions/2/2.11.tex}

\item In a school, there are 1000 students, out of which 430 are girls. It is known that out of 430,  10 percentage of the girls study in class XII. What is the probability that a student chosen randomly studies in Class XII given that the chosen student is a girl?\\
\solution
\input{solutions/2/2.12.tex}

\item A die is thrown three times. Events A and B are defined as below:\\
A : 4 on the third throw.\\
B : 6 on the first and 5 on the second throw.\\
Find the probability of A given that B has already occurred?\\
\solution
\input{solutions/2/2.13.tex}

\item A die is thrown twice and the sum of the numbers appearing is observed to be 6. What is the conditional probability that the number 4 has appeared at least once?\\
\solution
\input{solutions/2/2.14.tex}

\item Consider the experiment of tossing a coin. If the coin shows head, toss it again but if it shows tail, then throw a die. Find the conditional probability of the event that "the die shows a number greater than 4" given that "there is at least one tail".\\
\solution
\input{solutions/2/2.15.tex}

\item An urn contains 10 black and 5 white balls. Two balls are drawn from the urn one after the other without replacement. What is the probability that both drawn balls are black?\\

\item Three cards are drawn successively, without replacement from a pack of 52 well shuffled cards. What is the probability that first two cards are kings and the third card drawn is an ace?\\

\item A man is known to speak truth 3 out of 4 times. He throws a die and reports that it is a six. Find the probability that it is actually a six.\\

\item A person has undertaken a construction job. The probabilities are 0.65 that there will be strike, 0.80 that the construction job will be completed on time if there is no strike, and 0.32 that the construction job will be completed on time if there is a strike. Determine the probability that the construction job will be completed on time.\\
\solution
\input{./solutions/20-30/chapters/prob/examples/docq25.tex}

\item Bag I contains 3 red and 4 black balls while another Bag II contains 5 red and 6 black balls. One ball is drawn at random from one of the bags and it is found to be red. Find the probability that it was drawn from Bag II.\\
\solution
\input{./solutions/20-30/chapters/prob/examples/docq26.tex}

\item Given three identical boxes I, II and III, each containing two coins. In box I, both coins are gold coins, in box II, both are silver coins and in the box III, there is one gold and one silver coin. A person chooses a box at random and takes out a coin. If the coin is of gold, what is the probability that the other coin in the box is also of gold?\\
\solution
\input{./solutions/20-30/chapters/prob/examples/docq27.tex}

\item Suppose that the reliability of a HIV test is specified as follows: Of people having HIV, 90$\%$ of the test detect the disease but 10$\%$ go undetected. Of people free of HIV, 99$\%$ of the test are judged HIV –ve but 1$\%$ are diagnosed as showing HIV +ve. From a large population of which only 0.1$\%$ have HIV, one person is selected at random, given the HIV test, and the pathologist reports him/her as HIV +ve. What is the probability that the person actually has HIV?\\
\solution
\input{./solutions/20-30/chapters/prob/examples/docq28.tex}

\item In a factory which manufactures bolts, machines A, B and C manufacture respectively 25$\%$, 35$\%$ and 40$\%$ of the bolts. Of their outputs, 5, 4 and 2 percent are respectively defective bolts. A bolt is drawn at random from the product and is found to be defective. What is the probability that it is manufactured by the machine B?\\
\solution
\input{./solutions/20-30/chapters/prob/examples/docq29.tex}

\item A doctor is to visit a patient. From the past experience, it is known that the probabilities that he will come by train, bus, scooter or by other means of transport are respectively $\frac{3}{10},\frac{1}{5},\frac{1}{10}$ and $\frac{2}{5}.$ The probabilities that he will be late are $\frac{1}{4},\frac{1}{3}$ and $\frac{1}{12},$ if he comes by train, bus and scooter respectively, but if he comes by other means of transport, then he will not be late. When he arrives, he is late. What is the probability that he comes by train?\\
\solution
\input{./solutions/20-30/chapters/prob/examples/docq30.tex}

\item Coloured balls are distributed in four boxes as shown in Table \ref{table:1.43_boxes}

\begin{table}[ht!]
\centering
\input{./solutions/20-10/prob/tables/boxes43.tex}
\caption{Distribution of the balls in the boxes}
\label{table:1.43_boxes}
\end{table}
A box is selected at random and then a ball is randomly drawn from the selected box. The colour of the ball is black, what is the probability that ball drawn is from the box III?
\\
\solution
\input{./solutions/20-10/prob/chapters/exam43/solution.tex}

\item If a machine is correctly set up, it produces 90$\%$ acceptable items. If it is
incorrectly set up, it produces only 40$\%$ acceptable items. Past experience shows that
80$\%$ of the set ups are correctly done. If after a certain set up, the machine produces 2 acceptable items, find the probability that the machine is correctly setup.
\\
\solution
\input{./solutions/20-10/prob/chapters/exam47/solution.tex}

\item A bag contains a red ball, a blue ball and a yellow ball, all the balls being
of the same size.Kritika takes out a ball from the bag without looking into it. What is the probability that she takes out the
(i) yellow ball? \\
(ii) red ball?\\
(iii) blue ball?
\\
\solution
\input{./solutions/20-10/prob/chapters/exam49/solution.tex}
\item An urn contains 5 red and 5 black balls. A ball is drawn at random, its colour is noted and is returned to the urn. Moreover, 2 additional balls of the colour drawn are put in the urn and then a ball is drawn at random. What is the probability that the second ball is red?\\
\solution
\input{./solutions/40-50/probability/chapters/Q47/solution.tex}

\item A bag contains 4 red and 4 black balls, another bag contains 2 red and 6 black balls. One of the two bags is selected at random and a ball is drawn from the bag which is found to be red. Find the probability that the ball is drawn from the first bag.\\
\solution
\input{./solutions/40-50/probability/chapters/Q48/solution.tex}

\item Of the students in a college, it is known that 60$\%$ reside in hostel and 40$\%$ are day scholars (not residing in hostel). Previous year results report that 30$\%$ of all students who reside in hostel attain A grade and 20$\%$ of day scholars attain A grade in their annual examination. At the end of the year, one student is chosen at random from the college and he has an A grade, what is the probability that the student is a hostelier?\\
\solution
\input{./solutions/40-50/probability/chapters/Q49/solution.tex}

\item In answering a question on a multiple choice test, a student either knows the
answer or guesses. Let $\frac{3}{4}$ be the probability that he knows the answer and $\frac{1}{4}$ be the probability that he guesses. Assuming that a student who guesses at the answer will be correct with probability $\frac{1}{4}$. What is the probability that the student knows the answer given that he answered it correctly?\\
\solution
\input{./solutions/40-50/probability/chapters/Q50/solution.tex}

\end{enumerate}
