\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Find the remainder when $x^3-ax^2 +6x-a$ is divided by $x-a$.
\item Find the value of k, if x – 1 is a factor of p(x) in each of the following cases: 
\begin{enumerate}
\item $p(x) = x^2 + x + k$
\item $p(x) = kx^2-\sqrt{2}x+1$
\item $p(x) = 2x^2 + kx + \sqrt{2}$
\item $p(x) = kx^2  - 3x + k$
\end{enumerate}
\item Divide the polnyomial $p(x)$ by the polynomial $g(x)$ and find the quotient and remainder in each of the following:
\begin{enumerate}
\item $p(x) = x^3-3x^2+5x-3, g(x) = x^2-2$.
\item $p(x) = x^4-3x^2+4x+5, g(x) = x^2+1-x$.
\item $p(x) = x^4-5x+6, g(x) = 2-x^2$.
\end{enumerate}
\item Check whether the first polynomial is a factor of the second polynomial by dividing the second polynomial by the first polynomial:
\begin{enumerate}
\item $t^2-x,2t^4+3t^3-2t^2-9t-12$.
\item $x^2+3x+1, 3x^4+5x^3-7x^2+2x+2$.
\item $x^3-3x+1, x^5-4x^3+x^2+3x+1$.
\end{enumerate}
%
\item Obtain all the other zeroes of $3x^4+6x^3-2x^2-10x-5$, if two of its zeroes are $\sqrt{\frac{5}{3}}$and $-\sqrt{\frac{5}{3}}$.
\item On dividing $x^3-3x^2+x+2$ by a polynomial $g(x)$, the quotient and remainder were $x-2$ and $-2x+4$respectively.  Find $g(x)$.
\item Verify that the numbers given alongside the cubic polynomials below are their zeroes.  Also verify if the relationship between the zeroes and the coefficients in each case:
\begin{enumerate}
\item $2x^3+x^2-5x+2; \frac{1}{2}, 1, -2$
\item $x^3-4x^2+5x-2; 2, 1, 1$
\end{enumerate}
\item Find a cubic polynomial with the sum, sum of the product of its zeroes taken two at a time, and the product of its zeroes as 2, -7, -4 respectively.
\item If two zeroes of the polynomial $x^4-6x^3-26x^2+138x-35$ are $2\pm \sqrt{3}$, find the other zeroes.\item If the polynomial $x^4-6x^3+16x^2-25x+10$ is divided by another polynomial $x^2-2x+k$, the remainder comes out to be $x+a$, find $k$ and $a$.
\item The product of two consecutive positive integers is 306. We need to find the integers.
\item Rohan’s mother is 26 years older than him. The product of their ages (in years) 3 years from now will be 360. We would like to find Rohan’s present age.
\item A train travels a distance of 480 km at a uniform speed. If the speed had been 8 km/h less, then it would have taken 3 hours more to cover the same distance. We need to find the speed of the train.
\item Find two numbers whose sum is 27 and product is 182. 
\item  Find two consecutive positive integers, sum of whose squares is 365. 
\item  A cottage industry produces a certain number of pottery articles in a day. It was observed on a particular day that the cost of production of each article (in rupees) was 3 more than twice the number of articles produced on that day. If the total cost of production on that day was \rupee 90, find the number of articles produced and the cost of each article.\item The sum of the reciprocals of Rehman’s ages, (in years) 3 years ago and 5 years from now is $\frac{1}{3}$.  Find his present age.
\item In a class test, the sum of Shefali’s marks in Mathematics and English is 30. Had she got 2 marks more in Mathematics and 3 marks less in English, the product of their marks would have been 210. Find her marks in the two subjects.
\item The difference of squares of two numbers is 180. The square of the smaller number is 8 times the larger number. Find the two numbers.
\item A train travels 360 km at a uniform speed. If the speed had been 5 km/h more, it would have taken 1 hour less for the same journey. Find the speed of the train.
\item Two water taps together can fill a tank in 9$\frac{3}{ 8}$
hours. The tap of larger diameter takes 10
hours less than the smaller one to fill the tank separately. Find the time in which each tap can separately fill the tank.
\item An express train takes 1 hour less than a passenger train to travel 132 km between Mysore and Bangalore (without taking into consideration the time they stop at intermediate stations). If the average speed of the express train is 11km/h more than that of the passenger train, find the average speed of the two trains.
\item Sum of the areas of two squares is 468 $m^22$ find the sides of the two squares.
\item Find the values of k for each of the following quadratic equations, so that they have two equal roots:
\begin{enumerate}
\item 	$2x^2+kx+3 = 0$
\item 	$kx\brak{x-2}+6= 0$
\end{enumerate}
\item Is the following situation possible? If so, determine their present ages. The sum of the ages of two friends is 20 years. Four years ago, the product of their ages in years was 48.
\item If 
%
\begin{align}
\vec{x} = \sqrt{
\frac{\myvec{a\\-b}}{\myvec{c\\-d}}
}
\end{align}
%%
prove that 
%
\begin{align}
\norm{\vec{x}}^2 = \frac{
\norm{
\myvec{a\\b}
}
}
{
\norm{\myvec{c\\d}}
}
\end{align}
\item For any two complex numbers $\vec{z}_1, \vec{z}_2$, prove that 
%
\begin{align}
\Re{\vec{z}_1\vec{z}_2} = 
\Re{\vec{z}_1}
\Re{\vec{z}_2}-
\Im{\vec{z}_1}
\Im{\vec{z}_2}
\end{align}
\item If $\vec{x} = \frac{\myvec{a\\b}}{\myvec{a\\-b}}$, show that $\vec{\norm{x}} = 1$
%
\item If $\vec{x} = \frac{\myvec{x\\1}^2}{2x^2+1}$, prove that $\norm{\vec{x}}^2 = \frac{\brak{x^2+1}^2}{\brak{2x^2+1}^2}$.
%
\item If $\myvec{x\\y}^3 = \vec{u\\v}$, then show that $\frac{u}{x}+\frac{v}{y} = 4\brak{x^2-y^2}$.
\item If $\bm{\alpha}, \bm{\beta}$ are different complex numbers with $\norm{\bm{\beta}}=1$, then find $\norm{\frac{\bm{\beta}-\bm{\alpha}}{1-\bm{\alpha}^{*}\bm{\beta}}}.$
\item Find the number of non-zero integral solutions of the equation $\norm{1\\-1}^x = 2^x$ .
\item If $\myvec{ a\\ b}\myvec{c \\ d}\myvec{e \\ f}\myvec{g \\ h} = \myvec{A \\ B}$, then show that 
$\brak{a^2+b^2}\brak{c^2+d^2}\brak{e^2+f^2}\brak{g^2+h^2}=A^2+B^2$.
\item If $\brak{\frac{\myvec{1\\1}}{\myvec{1\\-1}}}=1$,  the find hte least positive integral value of $m$.
\item If a parabolic reflector is 20 cm in diameter and 5 cm deep, find the focus. 
\item An arch is in the form of a parabola with its axis vertical. The arch is 10 m high and 5 m wide at the base. How wide is it 2 m from the vertex of the parabola?
\item The cable of a uniformly loaded suspension bridge hangs in the form of a parabola. The roadway which is horizontal and 100 m long is supported by vertical wires attached to the cable, the longest wire being 30 m and the shortest being 6 m. Find the length of a supporting wire attached to the roadway 18 m from the middle.
\item An arch is in the form of a semi-ellipse. It is 8 m wide and 2 m high at the centre. Find the height of the arch at a point 1.5 m from one end.
\item A rod of length 12 cm moves with its ends always touching the coordinate axes. Determine the equation of the locus of a point P on the rod, which is 3 cm from the end in contact with the x-axis.
\item Find the area of the triangle formed by the lines joining the vertex of the parabola $x^2= 12y$ to the ends of its latus rectum.
\item A man running a racecourse notes that the sum of the distances from the two flag posts from him is always 10 m and the distance between the flag posts is 8 m. Find the equation of the posts traced by the man.
\item An equilateral triangle is inscribed in the parabola $y^2 = 4 ax$, where one vertex is at the vertex of the parabola. Find the length of the side of the triangle.
%
%
 \item Prove that the curves $x = y^2$ and $kx=y$ cut at right angles if $8k^2 = 1$

\item Find the equations of the tangent and normal to the parabola 
$y^2 = 4ax$ at the point $\myvec{at^2\\2at}$.
\item Find the equations of the tangent and normal to the hyperbola 
$
\vec{x}^T\myvec{\frac{1}{a^2} & 0 \\ 0 & -\frac{1}{b^2}}\vec{x} = 1
$
at the point $\myvec{x_0\\ y_0 }$.
\item  Find the area of the smaller part of the circle $\vec{x}^\vec{x}=a^2$ cut off by the line $x = \frac{a}{\sqrt{2}}$.
\item Find the area enclosed between the parabola $y^2=4ax$ ad the line $y = mx$.

\end{enumerate}
