%\renewcommand{\theequation}{\theenumi}
%\begin{enumerate}[label=\arabic*.,ref=\thesubsection.\theenumi]
%\numberwithin{equation}{enumi}
%
\item Rain is falling vertically with a speed of 35 $m s^{-1}$
. Winds starts blowing after sometime with a speed of 12 $m s^{-1}$ in
east to west direction. In which direction should a boy waiting at a bus stop hold his umbrella ?
%
\\
\solution 
\input{./solutions/1/chapters/line/Motion_plane/solution.tex}

\item A motorboat is racing towards north at 25 km/h and the water current in that region is 10 km/h in the direction of 60$\degree$ east of south. Find the resultant velocity of the boat.
\\
\solution 
\input{./solutions/2/chapters/line_ex/motion_in_a_plane/solution.tex}
\item Rain is falling vertically with a speed of 35 $m s^{-1}$
. A woman rides a bicycle with a speed of 12 $ms^{-1}$ in east to west
direction. What is the direction in which she should hold her umbrella ?
\\
\solution 
\input{./solutions/3/chapters/line/rain/solution.tex}
\item  A hiker stands on the edge of a cliff 490 m above the ground and throws a stone horizontally with an initial speed of 15 $m s^{-1}$
. Neglecting air resistance,
find the time taken by the stone to reach the ground, and the speed with which it hits the ground. (Take g = 9.8 $m s^{-2}$
).
\\
\solution 
\input{./solutions/4/chapters/line/motion/solution.tex}
\item Rain is falling vertically with a speed of 30 $m s^{-1}$. A woman rides a bicycle with a speed  of 10 $m s^{-1}$ in the north to south direction. What is the direction in which she should
hold her umbrella?
\\
\solution 
\input{./solutions/5/chapters/lines/docq12.tex}
\item A man can swim with a speed of 4.0 km/h in still water. How long does he take to cross a river 1.0 km wide if the river flows steadily at 3.0 km/h and he makes his strokes normal to the river current? How far down the river does he go when he reaches the other bank ?
\\
\solution 
\input{./solutions/6/chapters/line/motion_plane/solution.tex}
\item In a harbour, wind is blowing at the speed of 72 km/h and the flag on the mast of a boat anchored in the harbour flutters along the N-E direction. If the boat starts moving at a speed of 51 km/h to the north, what is the direction of the flag on the mast of the boat ?
\\
\solution 
\input{./solutions/7/chapters/line/motion/solution.tex}

%\end{enumerate}
